A Comparison of Graph Processing Systems

### 2020-09-20 documentation/paper/sections/overview/overview.tex
most introductions done

\section{Framework Overview}
The following paragraphs is a short overview describing functionality and characteristics of several state-of-the-art graph processing frameworks.
All of the described frameworks are part of our testing.
\todo

>>>>

\section{Framework Overview}
The following paragraphs are a short overview describing functionality and characteristics of several state-of-the-art graph processing frameworks.
All of the described frameworks are part of our testing.
\todo
